% Modified Jul 5,2013

\documentclass[10pt, letterpaper, oneside]{article}

\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage[dvipsnames]{color}
\usepackage{baskervald}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{etoolbox}

\pagestyle{plain}

\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}

%Bibliography Settings
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
\makeatletter
\def\@biblabel#1{}
\makeatother

% Name and contact information
\newcommand{\name}{Carlo Yuvienco}
\newcommand{\street}{37 Wall Street, Apt 16D}
\newcommand{\city}{New York NY }
\newcommand{\postal}{10005}
\newcommand{\phone}{(917) 607-5842 }
\newcommand{\email}{yuvienco@gmail.com}

% Colors
\definecolor{light-grey}{gray}{0.8}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Commands and Environments for resume

% A horizontal rule for sections
\newcommand{\HRule}[2]{\textcolor{#1}{\rule{\linewidth}{#2}}}

% A section tile command
\newcommand{\sectiontitle}[1]{\begin{minipage}{\textwidth}\HRule{black}{0.25mm}\vspace{-10pt}\begin{center}\Large\MakeUppercase{#1}\end{center}\end{minipage}\\\HRule{light-grey}{0.15mm}\vspace{\baselineskip}}

% An environment for a resume section
\newenvironment{ressection}[1]{
  \sectiontitle{#1}}
  {\vspace{-\baselineskip}}

% A ressection that has to be on one page, awards, education etc
\newenvironment{tightressection}[1]{
  \begin{minipage}{\textwidth}
  \sectiontitle{#1}}
  {\vspace{\baselineskip}\end{minipage}}

% A column if there is a two columned section such as in awards
\newenvironment{rescolumn}{
  \begin{minipage}{0.5\textwidth}
    \begin{itemize}[noitemsep,nolistsep]}
  {\end{itemize}
    \end{minipage}}

% A resitem is a simple list element
\newcommand{\resitem}[1]{
	\vspace{2pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% An entry for memberships
% Arg1: Board
% Arg2: Position
% Arg3: Date
\newcommand{\boardentry}[3]{
  \begin{minipage}{\textwidth}
  \vspace{-9pt}
  \textbf{#1}\\
  \textit{#2}, \textit{#3}\\
  \vspace{0.5\baselineskip}
  \end{minipage}
}


% An entry for education
% Arg1: Institution
% Arg2: Program
% Arg3: Dates
\newcommand{\resedentry}[3]{
  \begin{minipage}{\textwidth}
  \vspace{-10pt}
  \textbf{#1}\\
  \textit{#2}\hfill\textcolor{light-grey}{#3}\\
  \vspace{0.5\baselineskip}
  \end{minipage}
}

% Resentry defines a position
% Arg1: Position title
% Arg2: Company or Office---Company
% Arg3: Location, PROV
% Arg4: Date Range
\newcommand{\resentryheader}[4]{
	\vspace{-5pt}
	\textbf{#1}\hspace{\stretch{1}}\textcolor{light-grey}{#3}\\
	\textit{#2}\hspace{\stretch{1}}\textcolor{light-grey}{#4}\\
}

% This is a resume entry with a header and bullet items
\newenvironment{resentry}[4]{
  \begin{minipage}{\textwidth}
	\resentryheader{#1}{#2}{#3}{#4}
        \vspace{-\baselineskip}
	\begin{itemize}[noitemsep,nolistsep]
}{
	\end{itemize}
        \vspace{\baselineskip}
        \end{minipage}
}


%%%%%%%%%%%%
% Begin The Resume

\begin{document}

\begin{tabularx}{\linewidth}{X r}
\multirow{3}{*}
{\huge\textbf{\name}} & \street\\
& \city \postal\\
& \phone | \email\\
\end{tabularx}\\

% Education
\vspace{\baselineskip}
\begin{tightressection}{education}
  \resedentry{New York University}{Doctor of Philosophy (Biomedical Engineering)}{May 2010 --- May 2014}
  \resedentry{Polytechnic Institute of NYU}{Master of Science (Biomedical Engineering)}{September 2007 --- May 2010}
  \resedentry{The Cooper Union for the Advancement of Science and Art}{Bachelor of Engineering (Chemical Engineering)}{August 2001 --- May 2005}
\end{tightressection}

%Experience
\vspace{-\baselineskip}
\begin{ressection}{experience}
  \begin{resentry}{President, CEO}{inSchool Apps, LLC}{New York, NY}{June 2013 --- Present}
    \resitem{Command a Coast Guard fast rescue craft (FRC) and Coast Guard station.}
    \resitem{Responsible for the on-site training and direction of two crewmembers.}
    \resitem{Responsible to respond within 15 minutes as the primary marine search and rescue unit in our operational area to search and rescue taskings provided by the Joint Rescue Coordination Centre.}
    \resitem{Responsible for carrying out public search and rescue prevention programs such as Pleasure Craft Courtesy Checks and informational interviews.}
  \end{resentry}

  \begin{resentry}{NSF Graduate Research Fellow}{Polytechnic Institute of NYU}{Brooklyn, NY}{September 2008 --- May 2013}
    \resitem{Assist in the labs for a new third year electrical engineering project course.}
    \resitem{Act as a consultant for the students on topics relating to embedded hardware and software design.}
    \resitem{Assist in diagnosing technical problems and directing students to appropriate technical resources.}
  \end{resentry}

  \begin{resentry}{R \& D Scientist}{Pall Corporation}{East Hills, NY}{June 2005 --- August 2007}
    \resitem{Assist in the labs for a new third year electrical engineering project course.}
    \resitem{Act as a consultant for the students on topics relating to embedded hardware and software design.}
    \resitem{Assist in diagnosing technical problems and directing students to appropriate technical resources.}
  \end{resentry}

\end{ressection}

% Awards
\vspace{\baselineskip}
\begin{tightressection}{awards \& honors}
  \begin{rescolumn}
      \resitem{Four year, full tuition scholarship, The Cooper Union, 2001-2005}
      \resitem{Frank Caldiero Humanities Award, The Cooper Union, 2003}
      \resitem{Alpert Fellowship, The Cooper Union, 2003-2005}
      \resitem{41\textsuperscript{st} Annual MACUB Conference (Graduate) Poster Competition (1st place), 2008}
    \end{rescolumn}
  \begin{rescolumn}
      %\resitem{American Chemical Society Graduate Relations Officer, 2008-2009}
      \resitem{National Science Foundation Graduate Teaching Fellowship, 2008-2010}
      \resitem{NIH/NCI 2\textsuperscript{nd} Biennial Symposium: Chemical Insights into Biological Processes - Outstanding Poster Award, 2010}
      \resitem{8\textsuperscript{th} Annual Excellence in Polymer Graduate Research Symposium, 2012}
    \end{rescolumn}
\end{tightressection}

% Publications
\begin{tightressection}{publications}
    \vspace{-2\baselineskip}
    \nocite{*}
    \bibliographystyle{ieeetr}
    \bibliography{resume}
\end{tightressection}

% Presentations
\begin{tightressection}{presentations}
    \vspace{-2\baselineskip}
  \begin{itemize}[noitemsep,nolistsep]
    \resitem{Presentation: ``Design of an Open Source Hardware Sensor and Data Logging Unit''.  Presented at the National Conference on Undergraduate Research, University of Wisconsin - La Crosse, April 2013.}
    \resitem{Presentation of Unpublished Paper: ``Inside Everything: Strategies to Promote Taiwan's Continued Importance in the Global Semiconductor Market''. Presented at the National Chengchi University, Taipei, October 2012.}
  \end{itemize}
\end{tightressection}


\end{document}
